MNRAS \LaTeXe\ template -- title goes here

### 2017-10-26 Paper/paper.tex
Schechter - MF section

\section{Illustris Simulation}
Illustris-1, also known simply as Illustris, is a highly resolved
cosmological simulation. It reproduces large-scale statistical
features of the Universe, such as the galaxy population of massive
clusters, as well as small-scale properties such as the morphology of
galaxies and detailed values for their stellar and gas content.\\

@@

\section{The method}

@@

\subsection{The $3^{rd}$ nearest neighbor definition of environment}

@@

\subsection{The cosmic web method}
To complement and verify the analysis performed with the third nearest neighbor method, we chose a complementary method of completely different nature.

>>>>

\section{Illustris Simulation}
Illustris-1, also known as Illustris, is a highly resolved
cosmological simulation. It reproduces large-scale statistical
features of the Universe, such as the galaxy population of massive
clusters, as well as small-scale properties such as the morphology of
galaxies and detailed values for their stellar and gas content.\\

@@

\section{The methodology}

\subsection{ Characterizing Mass Functions}
A mass function is the number density $n(M)$ of objects of determined mass $M$.
Due to the large range of orders of magnitud in which these quantities span, the mass function is often represented in logarithmic scales on both sides. 
The discretization of these mass functions is simply the histogram of the logarithmic masses of the studied group of objects. 
In Illustris, as in all simulations, we have clear determination of volumes. This volume is constant over all the sample of galaxies studied and is to be taken the constant volume of the simulation $V = \left(106.5\text{Mpc}\right)^3$. 
In this sense, the relation expressed by a mass function is

\begin{equation}
n(M)Vd\log{(M)} =  dN
\end{equation}

To characterize specific properties of these mass functions, we use the Press-Schechter function \ref{eq:Schechter}. 
It comes from an elaborated formalism of hierarchical formation of DM structures in an expanding Friedmann universe arriving to a self-similar state of "equilibrium" for its mass function \cite{Schechter1976}.
Although its ansatz has been demonstrated to be inaccurate for our observable universe \cite{inaccurateSchechter}, the final expression is very well fitted to the mass functions of the local universe \cite{wellfitSchechter}.\\

\begin{equation}
n\left( M \right) = n_*\left( \frac{M}{M_*} \right)^{-\alpha+1}\exp^{-\left( \frac{M}{M_*}\right)}
\label{eq:Schechter}
\end{equation}

The Schechter function \ref{eq:Schechter} is fully defined by the three parameters $(n_*,M_*,\alpha)$. 
The number density factor $n_*$ is just a normalization factor which vary depending on the studied system. 
The mass scale factor $M_*$ may be interpreted as the mass that separates the power-law regimen $M \ll M_*$ and the exponential regimen $M \gg M_*$. 
This transition graphically resemnles a knee, which is the reason why $M_*$ is referred as the knee-mass.
The faint-end slope $\alpha$ is directly related to the exponent of the power-law at the low-mass regime.
In logarithmic scales, it is clearly interpreted as the slope of the low-mass regime.\\

We characterize each mass function with a Schechter
function \ref{eq:schechter}. It is . These parameters and their
respective estimated errors are determined with a MCMC fit
applied directly to the MF.\\

@@

\subsection{Defining the environment}

\subsubsection{The $3^{rd}$ nearest neighbor definition of environment}

@@

\subsubsection{The cosmic web method}
To complement and verify the analysis performed with the third nearest neighbor method, we chose a complementary method of completely different nature.
